---
title: "Portfolio 4"
---

The purpose of this project is to work with data visualizations for new data, and manipulating the data frame in order to show what I want to know. It's mainly just me playing around with data so I can become more comfortable with data frames and finding out what I can learn from the data and the visuals I can create.

Note: I got this data set from: https://github.com/justmarkham/pandas-videos

```{r load_data}
library(tidyverse)
library(dplyr)
library(broom)
library(openintro)
library(ggplot2)
drinks <- read_csv("C:/Users/rgood28/Documents/Data Sci Labs/extra_datafiles/data/drinks.csv")
```

```{r beer_by_continent}
ggplot(data = drinks, mapping = aes(continent, beer_servings))+
  geom_col()+
  labs(title = "Beer Servings by Continent")

ggplot(data = drinks, mapping = aes(continent, wine_servings))+
  geom_col()+
  labs(title = "Wine Servings by Continent")

ggplot(data = drinks, mapping = aes(continent, spirit_servings))+
  geom_col()+
  labs(title = "Spirit Servings by Continent")
```

```{r count_continent}
ggplot(data = drinks, mapping = aes(continent))+
  geom_bar()
```


I spent too much time trying to figure out how to reorder the columns so that they went in numerical order... that was the goal but I am running out of time, and this is only my 4th portfolio. So I changed to color to show beer_servings greater than 300... Germany and Ireland were among those unsurprisingly.

```{r europe_beer}
europe_beer <- drinks %>% filter(
  continent == "Europe",
  beer_servings > 100
)

ggplot(data = europe_beer, mapping = aes(country, beer_servings, fill = beer_servings> 300))+
  geom_bar(stat = "identity")+
  coord_flip()

```

Portugal, France, and Andorra drink the most wine. I am honestly surprised that Italy is not as high up.

```{r europe_wine}
europe_wine <- drinks %>% filter(
  continent == "Europe",
  wine_servings > 100
)

ggplot(data = europe_wine, mapping = aes(country, wine_servings, fill = wine_servings > 300))+
  geom_bar(stat = "identity")+
  coord_flip()

```

Belarus drinks the most liquor.


```{r europe_spirit}
europe_spirit <- drinks %>% filter(
  continent == "Europe",
  spirit_servings > 100
)

ggplot(data = europe_spirit, mapping = aes(country, spirit_servings, fill = spirit_servings > 300))+
  geom_bar(stat = "identity")+
  coord_flip()
```