---
title: "Portfolio 6"
author: "Rachel Good"
date: "`r Sys.Date()`"
---

The goal of this portfolio is to learn how to loop in R. I am using one of the activities from my Python class as a model for what I should learn. I am going to see what the major differences (if any) there are in loops between Python and R.

### First Exercise

Python code to model:
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i < 3:
  print(i)
  # update loop variable to avoid infinite loop
  i = i + 1
  
```{r loop1}
i <- 0
while (i < 3) {
  print(i)
  i <- i + 1
}
```

### Second Exercise

Python code to model:
num_input = int(input())
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i <= num_input:
  print(i)
  i += 1

  # update loop variable to avoid infinite loop


This is the first time I have learned how to ask for an input in R. It's interesting to compare this to Python as in Python the function "readlines" is used to read lines from a file to output as a list by line, rather than a running string.

While loops in general seem very similar between R and Python, the major difference is just formatting i.e., having to use parentheses for the while statement, using braces instead of a colon to signal the code to perform during the while loop.
```{r loop2}
num_input = readline()
num_input = as.integer(num_input)
i <- 0
while (i < num_input) {
  print(i)
  i <- i + 1
}
```

### Third Exercise

Python code to model:
my_list = ['a', 'b', 'c']
# find length of my_list
length = len(my_list)
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i <= length:
  print(i)
  i += 1

  # update loop variable to avoid infinite loop
