---
title: "Portfolio 6"
author: "Rachel Good"
date: "`r Sys.Date()`"
---
### While Loops
Note: Because this code asks for input, you cannot knit the Rmd.

The goal of this portfolio is to learn how to do while loops in R. I am using one of the activities from my Python class as a model for what I should learn. I am going to see what the major differences (if any) there are in loops between Python and R.

### Exercise 1

Python code to model:
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i < 3:
  print(i)
  # update loop variable to avoid infinite loop
  i = i + 1
  
```{r loop1}
i <- 0
while (i < 3) {
  print(i)
  i <- i + 1
}
```

### Exercise 2

Python code to model:
num_input = int(input())
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i <= num_input:
  print(i)
  i += 1

  # update loop variable to avoid infinite loop


This is the first time I have learned how to ask for an input in R. It's interesting to compare this to Python as in Python the function "readlines" is used to read lines from a file to output as a list by line, rather than a running string.

While loops in general seem very similar between R and Python, the major difference is just formatting i.e., having to use parentheses for the while statement, using braces instead of a colon to signal the code to perform during the while loop.
```{r loop2}
num_input = readline()
num_input = as.integer(num_input)
i <- 0
while (i < num_input) {
  print(i)
  i <- i + 1
}
```

### Exercise 3

Python code to model:
my_list = ['a', 'b', 'c']
# find length of my_list
length = len(my_list)
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i <= length:
  print(i)
  i += 1

  # update loop variable to avoid infinite loop

```{r loop3}
my_list <- c('a', 'b', 'c')
length <- length(my_list)
i <- 0
while (i < length) {
  print(i)
  i <- i + 1
}
```

### Example 4

Python code to model:
word_input = input()
# find length of word_input
length1 = len(word_input)
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i <= length1:
  print(i)
  i += 1

  # update loop variable to avoid infinite loop
  
```{r loop4}
word_input = readline()
word_length = str_length(word_input)
i <- 0
while (i <= word_length) {
  print(i)
  i <- i + 1
}
```

### Exercise 5

Python code to model:
# define a loop variable
i = 0
# create a while statement with a Boolean expression
while i <= 10:
  # if loop variable is greater than 5, break from loop
  if i > 5:
    break
  # update loop variable to avoid infinite loop
  i += 1
  print(i)
  
```{r loop5}
i <- 0
while (i <= 10) {
  if (i > 5) {
    break
  }
  print(i)
  i <- i + 1
}
```

### Exercise 6

Python code to model:
# define a loop variable
word_input2 = input()

# create a while statement with a Boolean expression
while word_input2 != "stop":
  print(word_input2)
  word_input2 = input()

  # update loop variable to avoid infinite loop
  
  
I had to change the word from stop to done because stop is a command in the console so it was weird.
```{r loop6}
word_input2 <- readline()
while (word_input2 != "done") {
  print(word_input2)
  word_input2 <- readline()
}
```

### Exercise 7

Python code to model:
# create empty list
my_list2 = []
# find length of list

# create a while statement with a Boolean expression
while list_length < 3:
  new_item = input()
  my_list2.append(new_item)
  # update list to avoid infinite loop
  list_length = len(my_list2)
  print(my_list2)
  

This chunk of code did not like me. This should work according to google, however it has become an infinite loop and every time I input something for new_item, the console says "NULL". I tried creating an empty list first then putting items in the list to start. Neither worked. I also tried to specify the index to add the new item to, even though that isn't required. Also did not work. I eventually gave up due to time.
```{r loop7}
my_list2 <- c(1)
list_length <- length(my_list2)
while (list_length < 5) {
  new_item <- readline()
  my_list2 <- append(my_list2, new_item, after = index)
  list_length <- length(my_list2)
  print(my_list2)
}
```