---
title: "Portfolio 7"
author: "Rachel Good"
date: "`r Sys.Date()`"
---

### For Loops
Note: Because this code asks for input, you cannot knit the Rmd.

The goal of this portfolio is to learn how to do foor loops in R. I am using one of the activities from my Python class as a model for what I should learn. I am going to see what the major differences (if any) there are in loops between Python and R. 

### Exercise 1:
Python code to model:
my_list = ['a', 'b', 'c']

# create a for statement with a loop variable
for i in my_list:
  # print each element
  print(i)
  
```{r loop1}
for_list <- c('a', 'b', 'c')
for (i in for_list) {
  print(i)
}
```

### Exercise 2
Python code to model:
my_list = [1, 2, 3]

# create a for statement with a loop variable
for num in my_list:
  # multiply each element by 2
  num *= 2
  # print the product
  print(num)
  
```{r loop2}
num_list <- c(1, 2, 3)
for (i in num_list) {
  num = i * 2
  print(num)
}
```

### Exercise 3
Python code to model:
word = input()

# create a for statement with a loop variable
for chr in word:
  #print the character
  print(chr)
 
 
In R, we have to split the string in order to iterate through each character, unlike in Python, it automatically iterates throught the characters in a string.  
```{r loop3}
my_str = readline()
split_my_str <- strsplit(my_str, "")[[1]]

for (i in split_my_str) {
  print(i)
}
```

### Exercise 4
Python code to model:
my_list = [1, 2, 3]

# create a for statement with a loop variable
for num in my_list:
  # print out if each element is even or odd
  if num % 2 == 0:
    print('even')
  if num % 2 != 0:
    print('odd')


The modulo factor in R is %%, but in python it's only %  
```{r loop4}
for (i in num_list) {
  if (i %% 2 == 0) {
    print('even')
  } else {
    print('odd')
  }
}
```

### Exercise 5
Python code to model:
# Loop through the range of numbers from 0 to 5 (including 5) and print each number
# create a for statement with a loop variable using range(start, stop (not included), step)
for i in range(6):
  # print each number
  print(i)
  

In Python, you have to add 1 to the range, so 6 for 1-5. 
```{r loop5}
for (i in 1:5) {
  print(i)
}
```

### Exercise 6
Python code to model: