---
title: "Portfolio 9"
author: "Rachel Good"
date: "`r Sys.Date()`"
---

Attempting Lab from Module 12

```{r load_packages}
library(tidyverse) 
library(infer)
library(openintro)
library(ggplot2)
```

```{r load_data}
data(ncbirths)
nrow(ncbirths)
summary(ncbirths)
```

### Exercise 1

Each case is a pregnancy case - so mom and baby. There are 1000 cases.
Numerical: fage, mage, weeks, visits, gained, weight
Categorical: Mature, premie, marital, lowbirthweight, gender, habit, whitemom
Weight gained by the mother appears to have an outlier at 85 lbs. Birth weight has a low outlier at 1lb, and weeks at 20.

### Exercise 2

Average birth weight for babies of white moms: 7.25 lbs
```{r white_moms}
ncbirths_white <- ncbirths %>% 
  filter(whitemom == "white")

mean(ncbirths_white$weight, na.rm = TRUE)
```

### Exercise 3
So I got confused after exercise 2 while trying to do portfolios after midnight. So now I am just planning to play around with the data and see what I can do with it. I am diverting course from the lab though.

Average birth weight for babies with non white mothers: 6.72 lbs
```{r do_something}
ncbirths_nonwhite <- ncbirths %>% 
  filter(whitemom != "white")

mean(ncbirths_nonwhite$weight, na.rm = TRUE)
```

```{r smokers}
ggplot(data = ncbirths, mapping = aes(weeks, weight, color = habit))+
  geom_jitter()

ggplot(data = ncbirths, mapping = aes(weeks, weight, color = habit))+
  geom_point()+
  facet_wrap(~habit)
```

adjusted r-squared: .0038
```{r smoker_model}
m_smoker <- lm(weight ~ habit, data = ncbirths)
summary(m_smoker)
```
```{r weeks}
m_weeks <- lm(weight ~ weeks, data = ncbirths)
summary(m_weeks)

```
```{r graph_regression}
ggplot(data = ncbirths, mapping = aes(weeks, weight))+
  geom_jitter()+
  geom_abline(intercept = -6.09529, slope = .34433)
```

adjusted r-squared: .4542
habit smoker now actually has a lesser p-value. Weeks is definitely predictive of weight. We wouldn't need to even add the variable about being a premie since weeks accounts for that.
```{r smoker_weeks}
smoker_weeks <- lm(weight ~ habit + weeks, data = ncbirths)
summary(smoker_weeks)
```

adjusted r-squared: .4592
```{r mage}
m_mage <- lm(weight ~ habit + weeks + mage, data = ncbirths)
summary(m_mage)
```

adjusted r-squared: .4595
```{r mage}
m_mage_gained <- lm(weight ~ habit + weeks + mage + gained, data = ncbirths)
summary(m_mage_gained)
```

adjusted r-squared: .444 (so let's take out fage)
```{r fage}
m_fage <- lm(weight ~ habit + weeks + mage + gained + fage, data = ncbirths)
summary(m_fage)
```

adjusted r-squared: .4646
```{r white}
m_white <- lm(weight ~ habit + weeks + mage + gained + whitemom, data = ncbirths)
summary(m_white)
```
