---
title: "Portfolio 10"
author: "Rachel Good"
date: "`r Sys.Date()`"
---

Goal: playing with more data.This data looks at the importance of selective attention in certain occupations.

Note: Data taken from https://www.onetonline.org/find/descriptor/result/1.A.1.g.1


After thoughts: So I thought this csv file I found would be more interesting and have more I could do with it. I thought the job zone maybe categorized the occupations by different types of jobs. However, it only looks at the amount of preparation needed. 

```{r load_packages}
library(tidyverse)
library(dplyr)
library(broom)
library(openintro)
library(ggplot2)

```

```{r load_data}
df_data <- read_csv("C:/Users/rgood28/Documents/Data Sci Labs/template_portfolio/selective_attention.csv")
```
```{r column_names}
colnames(df_data) <- c("importance", "level", "job_zone", "code", "occupation")
```

```{r job_zone}
df_data <- df_data %>% 
  mutate(zone = case_when(
    job_zone == 1 ~ "little or no prep",
    job_zone == 2 ~ "some prep",
    job_zone == 3 ~ "medium prep",
    job_zone == 4 ~ "considerable prep",
    job_zone == 5 ~ "extensive prep"))
```

```{r do_something}
ggplot(data = df_data, mapping = aes(importance, level, color = zone))+
  geom_jitter()

ggplot(data = df_data, mapping = aes(importance, level, color = zone))+
  geom_jitter()+
  facet_wrap(~zone)
```

```{r counts}
ggplot(data = df_data, mapping = aes(zone, fill = zone))+
  geom_bar()
```
```{r model}
model1 <- lm(importance ~ job_zone, data = df_data)
summary(model1)
```